Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-04-07 paper.tex
new figure included

\begin{figure}\footnotesize
    \centering
    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
     & Unplanned by the robot & Planned by the robot \\ \hline
    Perceived as non-intentional & case I  & case IIIa  \\ \hline
    Perceived as intentional &  case IIIb & case II 
    \end{tabular}
\caption{
    Behaviors of the robot that are unexpected by the user may be intentional
    (the robot has planned the behavior) or not (typically, a failure:
    misdetection, bug,...). Independently of that, the behavior may be
    \emph{perceived} by the user as intentional or not.}
\label{fig:perceptionUnexpectedBehavior}
\end{figure}

>>>>

%\begin{figure}\footnotesize
%    \centering
%    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
%     & Unplanned by the robot & Planned by the robot \\ \hline
%    Perceived as non-intentional & case I  & case IIIa  \\ \hline
%    Perceived as intentional &  case IIIb & case II 
%    \end{tabular}
%\caption{
%    Behaviors of the robot that are unexpected by the user may be intentional
%    (the robot has planned the behavior) or not (typically, a failure:
%    misdetection, bug,...). Independently of that, the behavior may be
%    \emph{perceived} by the user as intentional or not.}
%\label{fig:perceptionUnexpectedBehavior}
%\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.75\columnwidth]{un-expected-behavior.pdf}
    \caption{Behaviors of the robot that are unexpected by the user may be intentional
    (the robot has planned the behavior) or not (typically, a failure:
    misdetection, bug,...). Independently of that, the behavior may be
    \emph{perceived} by the user as intentional or not.}

    \label{fig:perceptionUnexpectedBehavior}
\end{figure}
